A general and efficient representation of ancestral recombination graphs

### 2024-06-10 paper.tex
Add postcodes

\affil[1]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, University of Oxford, OX3 7LF, UK}
\affil[2]{School of Mathematics and Statistics, University of Glasgow, UK}
\affil[3]{Department of Statistics, University of Oxford, UK}
\affil[4]{School of Mathematics, Statistics and Physics, Newcastle University, UK}
\affil[5]{Department of Statistics, University of Warwick, UK}
\affil[6]{The Roslin Institute and Royal (Dick) School of Veterinary Studies, University of Edinburgh, UK}
\affil[7]{Broad Institute of MIT and Harvard, Cambridge, USA}
\affil[8]{Department of Genetics, Stanford University School of Medicine, Stanford, USA}

>>>>

\affil[1]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, University of Oxford, OX3 7LF, UK}
\affil[2]{School of Mathematics and Statistics, University of Glasgow, G12 8TA, UK}
\affil[3]{Department of Statistics, University of Oxford, OX1 3LB, UK}
\affil[4]{School of Mathematics, Statistics and Physics, Newcastle University, NE1 7RU, UK}
\affil[5]{Department of Statistics, University of Warwick, CV4 7AL, UK}
\affil[6]{The Roslin Institute and Royal (Dick) School of Veterinary Studies, University of Edinburgh, EH25 9RG, UK}
\affil[7]{Broad Institute of MIT and Harvard, Cambridge, MA 02142, USA}
\affil[8]{Department of Genetics, Stanford University School of Medicine, Stanford, CA 94305-5101, USA}
